The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications

### 2016-01-31 DishSimulations/paper/DishSimulationsPaper_v3.tex
incorporated Rich's information into simulations paper draft. Still need to add two numbers

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
\altaffiltext{7}{Stellenbosh}
Tempe AZ}
\begin{abstract}
We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA). These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization. Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band. Overall, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.2$\,$h$Mpc$^{-1}$. Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array. 
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}. Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results. The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}. While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument. Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.

The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}. Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish. A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination since one cannot rely on direction independent redundant calibration to remove any spectral structure that varies as a function of location on the primary beam.

This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multifaceted approach for assessing whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and Orbcomm beam mapping \citep{Neben:2016}. In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field by \cite{Patra:2016}.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function. In \S~\ref{sec:SimulationResults} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}. In \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples at higher frequencies. Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. A simple equation describing effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver on a visibility has been derived in \citet{EwallWice:2015a}. We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element. 
We start by denoting the electric field of radiation arriving at an $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.

@@

A correlator measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{align}
V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
 &= \int d \Omega d \tau d \tau' \ftr_i(\tau) \ftr^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{align}
where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$. Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.

Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
\begin{equation}\label{eq:Visibility}
V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
\end{equation}
where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry. $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.

In order to filter spectrally smooth foregrounds from the signal,HERA is expected to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}

@@

which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$. In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines in $b-\tau$ space. Withthe reflections, the sources are smeared out, leading to supra-horizon emission. 

@@

\caption{A demonstration of the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission. Sources near zenith (low delay) tend to have a larger maximum since the beam gain is larger near zenith, but a more compact kernel (since beam bore-sights tend to have less spectral structure). Meanwhile, sources near the horizon have a much smaller maxima but have less compact kernels.}

@@

For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$. For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i(\bl)$. In this situation, we have

@@

where $V_{ij}$ is the visibility with the achromatic factor in the voltage patterns included. 

@@

Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument. This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel to be proportional to the square of the delay-response. This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in the regions of delay space that we want to measure the signal.

@@

HERA \citep{DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12) \citep{Pober:2014}. Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa. HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost. It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge. Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes. In Fig.~\ref{fig:AntennaComparison} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
\caption{The HERA antenna element (bottom) uses a parabolic dish to achieves over an order of magnitude increase in collecting area over the PAPER antenna (top). The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish. The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
\label{fig:AntennaCompare}
\end{figure}

\subsection{The Simulations}\label{ssec:Simulations}
We perform time-domain simulations of the voltage output of the HERA feed using CST. {\bf \color{red} Rich: fill in the details here, describe the CST parameters and a brief overview of how it numerically solves for the voltages (citations?).  }

In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. A $150$\,MHz plane wave with a Gaussian envelope with FWHM of {\bf \color{red}???} is initialized {\bf \color{red} ??} meters above the dish vertex traveling in the $-z$ direction. It is reflected by the dish before entering the dipole feed, hidden below the cylindrical skirt in this figure. We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the voltage at the feed outputs (black line). The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back. However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly with delay due to reflections within the dish-feed structure reintroducing the signal at times beyond its initial falloff. We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
\begin{figure}
\includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
\caption{A rendering of our time domain simulation at $t=0$, demonstrating the geometry and setup of our electromagnetic simulation. The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
\end{figure}

\begin{figure*}
\includegraphics[width=\textwidth]{figures/SimulationIllustration.png}
\caption{An illustration of our simulation products and their origin in the HERA antenna geometry. A plane wave is injected from above the feed (red line). The amplitude of the electric field of the plane wave at output of the feed along with the voltage at the feed terminal outputs is recorded (black line). The feed in our simulation is situated $5$\,m above the bottom of the dish, hence there is a $\approx 30$\,ns delay between when the plane wave passes the terminal for the first time (A) and when it is first absorbed in the dipole (B), leading to the voltage response. Of concern to 21\,cm experiments are the subsequent reflections between the feed and the dish (C) which can lead to large delay contamination of the EoR window.}
\label{fig:SimulationOutput}
\end{figure*}
\subsection{Deconvolving the Response Function}\label{ssec:Deconvolve}

We can do much better than this. From equation~\ref{eq:Voltage}, we know that the voltage output results from the convolution of the plane wave input with the voltage gain of the antenna. The voltage response of the dish which we are attempting to probe has been convolved with a known kernel; our input plane wave. Hence, a straightforward application of the Fourier convolution theorem allows us to determine the voltage response.

>>>>

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
\altaffiltext{7}{Stellenbosh}
Tempe AZ}
\begin{abstract}
We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA). These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization. Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band. We find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$. Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array. 
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). Two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}. Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results. The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}. While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument without deferring to a model. Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.

The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}. Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish. A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination.

This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multi-pronged campaign to assess whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}. In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function. In \S~\ref{sec:Results} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}. In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's ability to constrain reionization parameters. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window. Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument. Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples with shorter periods. Isolation of the 21\,cm signal from foregrounds that are over four orders of magnitude brighter depends critically on their smoothness. Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself. A simple equation describing effect of direction independent reflections in the signal chain downstream of the feed, has been derived in \citet{EwallWice:2015a}. We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element. 
We start denote the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.

@@

The correlator of a radio interferometer records the time-averaged product of the Fourier transfored voltage streams of the $i^{th}$ and $j^{th}$ antennas. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{align}
V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
 &= \int d \Omega d \tau d \tau' \ftr_i(\bl,\tau) \ftr^*_j(\bl,\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{align}
where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$. Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.

Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
\begin{equation}\label{eq:Visibility}
V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
\end{equation}
where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ and $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish. From equation~\ref{eq:Visibility} we see that $r_i(\bl,f)$ is precisely the voltage beam of the antenna. Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.

In order to filter spectrally smooth foregrounds from the signal, numerous experiments expect to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}

@@

which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$. In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility. Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays. We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources. Without reflections, the sources would form lines in $b-\tau$ space. With the reflections, the sources are smeared out, leading to supra-horizon emission. 

@@

\caption{A cartoon demonstration of the impact on foregrounds of the frequency dependent beam. Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element). Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}. Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line. We see that this smearing can lead to substantial supra-horizon emission.}

@@

For the sake of simplicity, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$. For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i(\bl)$. In this situation, we have

@@

where $V_{ij}$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 

@@

Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument. This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel is proportional to the square of the delay-response. This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall five to six orders of magnitude in the regions of delay space that we want to measure the signal.

@@

HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12). Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa. HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost. It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge. Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes. In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top). The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish. The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
\label{fig:AntennaCompare}
\end{figure}

\subsection{The Simulations}\label{ssec:Simulations}
 The time-dependent electromagnetic behavior of the antenna was modeled using Microwave Studio, a commercial numerical simulation package produced by Computer Simulation Technology (CST).  The model consists of an idealized 14 m diameter paraboloid reflector with a feed structure placed at the focus (4.5 m above the surface). The feed was a dual linear polarized sleeved dipole identical to that used as an element of PAPER but with a cylindrical skirt used in place of the angled planar reflectors.   The dipole arms were modeled as copper tubing and aluminum was assigned to the disks and reflector surfaces.  For simulation, the entire model was encapsulated in vacuum dielectric with radiative boundaries and discrete ports of 125\,$\Omega$ impedance were defined at the terminals of the orthogonal dipoles.

Microwave Studio divides the model into approximately 94 million discrete hexahedral cell,s where the field is calculated over time using Finite Integration Technique incorporating the Perfect Boundary Approximation \citep{CST} in response to a 100-200 MHz broadband pulse of about 40 ns in duration.  The model was excited in two ways: 1) via a plane wave entering the model along the bore sight, and 2) from one of the discrete terminals (whose analysis we focus on in \S~\ref{ssec:S11}).   The voltage responses at the terminals are monitored for these two cases over a duration of 500 ns as the excitation pulse travels throughout the model.

In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. A $150$\,MHz plane wave with a Gaussian envelope with FWHM of {\bf \color{red}???} is initialized {\bf \color{red} ??} meters above the dish vertex traveling in the $-z$ direction. It is reflected by the dish before entering the dipole feed, hidden below the cylindrical skirt in this figure. We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the voltage at the feed outputs (black line). The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back. However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly due to reflections within the dish-feed structure. We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
\begin{figure}
\includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
\caption{A rendering of our simulation setup at $t=0$. The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
\end{figure}

\begin{figure*}
\includegraphics[width=\textwidth]{figures/SimulationIllustration.png}
\caption{An illustration of our simulation products and their origin in the HERA antenna geometry. A plane wave is injected from above the feed. The electric field of the plane wave at the feed terminals (red line) along with the voltage output is recorded (black line). The feed in our simulation is situated $5$\,m above the bottom of the dish, hence there is a $\approx 30$\,ns delay between when the plane wave passes the terminal for the first time (A) and when it is first absorbed in the dipole (B), leading to the voltage response. Of concern to 21\,cm experiments are the subsequent reflections between the feed and the dish (C) which can lead to large delay contamination of the EoR window.}
\label{fig:SimulationOutput}
\end{figure*}
\subsection{Deconvolving the Response Function}\label{ssec:Deconvolve}
